Case study validations of automatic bullet matching

### 2018-10-23 index.Rmd
land to land scores

### Comparison of land-to-land scores

\hh{XXX error rates on land to land matches? XXX}

```{r, cache=TRUE}
hounest <- hounest %>% mutate(
  data = data %>% purrr::map(
    .f = function(d) {
      d$sameland = bullet_to_land_predict(
        land1 = d$land1, land2 = d$land2, 
        d$rfscore, difference=0.1)
      d
    })
)
houlands <- hounest %>% unnest(data)

@@

```{r rocs, fig.caption="ROC curves for all studies based on land-to-land comparisons."}
library(plotROC)
library(pROC)
all_lands %>% 
  ggplot(aes(colour = interaction(study, group1))) +
  geom_roc(aes(m = rfscore, d = as.numeric(sameland)), 
           labels =FALSE, pointsize = 0) 
```

```{r aucs, results="asis"}
aucs <- all_lands %>% group_by(study, group1) %>% nest() %>%
  mutate(
    auc_rf = data %>% purrr::map_dbl(function(d) {
      auc(d$sameland, d$rfscore)
    }),
    auc_ccf = data %>% purrr::map_dbl(function(d) {
      auc(d$sameland, d$ccf)
    })

@@

>>>>

# Digging deeper: comparison of land-to-land scores

\hh{XXX error rates on land to land matches? ROC curves in \autoref{fig:rocs} and corresponding AUC results for all studies in \autoref{tab:rocs} XXX}

```{r, cache=TRUE}
hounest <- hounest %>% mutate(
  data = data %>% purrr::map(
    .f = function(d) {
      d$sameland = bullet_to_land_predict(
        land1 = d$land1, land2 = d$land2, 
        d$rfscore, difference=0.05)
      d
    })
)
houlands <- hounest %>% unnest(data)

@@

```{r rocs, fig.caption="ROC curves for all studies based on land-to-land comparisons.", fig.width = 4.5, fig.height = 3, out.width = ".5\\textwidth"}
library(plotROC)
library(pROC)
all_lands %>% 
  ggplot(aes(colour = interaction(study, group1, sep = " "))) +
  geom_roc(aes(m = rfscore, d = as.numeric(sameland)), 
           labels =FALSE, pointsize = 0, alpha = 0.8) +
  theme_bw() +
  xlab("Fraction False Positives") +
  ylab("Fraction True Positives") +
  scale_colour_manual("Study", values = c("#fe9929", "#8856a7",
                                         "#74a9cf", "#2b8cbe", "#045a8d"))
```

```{r aucs, eval = FALSE}
aucs <- all_lands %>% group_by(study, group1) %>% nest() %>%
  mutate(
    auc_rf = data %>% purrr::map_dbl(function(d) {
      auc(d$sameland, d$rfscore)
    }),
    auc_ccf = data %>% purrr::map_dbl(function(d) {
      auc(d$sameland, d$ccf)
    })

@@

\begin{table}[ht]
\centering
\begin{tabular}{llrr}
  \hline
\bf study & \bf set & \bf AUC(RF score) & \bf AUC(Cross-correlation) \\ 
  \hline
\bf Hamby 44 &  & 0.956 & 0.926 \\ 
\bf   Phoenix PD &  & 0.976 & 0.986 \\ 
\bf   Houston FSI & G1 & 0.991 & 0.988 \\ 
\bf   Houston FSI & G2 & 0.898 & 0.902 \\ 
\bf   Houston FSI & G3 & 0.986 & 0.987 \\ 
   \hline
\end{tabular}
\caption{Area under the curve (AUC) for each (set) of the studies. As seen in the ROC curves, the algorithm performs the least well on set 2 of the Houston FSI study. Overall the perform on all sets is very good to excellent.
At the land level there is no difference in prediction power between RF score and cross-correlation.} 
\end{table}
